A simple and efficient algorithm for computing approximate Nash equilibria in sequential games with imcomplete information

### 2015-07-25 paper.tex
first WINE submission

\title{
  %\hrule\hrule\bigskip\bigskip
  A simple and efficient algorithm for computing approximate
  Nash equilibria in sequential games with imcomplete
  information}
\author{Elvis DOHMATOB%, Gael VAROQUAUX, Bertrand THIRION
\\\\Parietal team, Inria Saclay Ile-de-France, Saclay, France
\\\texttt{firstname.lastname@inria.fr}
}

@@

\maketitle
\begin{abstract}We present a simple primal-dual algorithm for
  computing approximate Nash equilibria in two-person zero-sum
  sequential games with  imcomplete information and perfect recall
  (like Texas Hold'em Poker). Our algorithm only performs basic
  iterations (i.e iterations involving no calls to external
  first-order oracles, etc.)
  and is applicable to a broad class of two-person zero-sum games
  including simultaneous games and sequential games with imcomplete
  information and perfect recall. The applicability to the latter kind
  of games is thanks to the sequence-form representation
  \cite{koller1992complexity} which allows us to encode any such game
  as a matrix game with polyhedral strategy profiles. We prove that
  the number of iterations needed to produce a Nash equilibrium with a
  given precision is inversely proportional to the
  precision. We also present experimental results on simulated and
  real games (Kuhn poker).
\end{abstract}

\textbf{keywords}: sequential game; imcomplete information; perfect
recall; approximate Nash equilibrium; primal-dual
algoithm; convex-optimization

\section{Introduction}
\label{sec:intro}
A game-theoretic approach to playing games strategically optimally
consists in computing Nash-equilibria (infact, approximations thereof)
offline, and playing one's part (an optimal \textit{behavioral}
strategy) of the equilibrium online. This
technique is the driving-force behind solution concepts like CFR
\cite{zinkevich2008regret,lanctot2009monte},
$\text{CFR}^{+}$ \cite{tammelin14} and other variants, etc., which
have recently had profound success in Poker. However, solving games
for equilibria remains a mathematical and computational challenge,
especially in sequential games with imperfect information. This paper
proposes a simple and fast algorithm for solving for such equilibria
approximately, in a sense which will be made clear shortly.

@@

\subsection{Nash-equilibrium concepts and statement of the problem}
The sequence-form representation for two-person zero-sum games with
imcomplete information was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium} where it was
established that for such games, there exist sparse matrices
$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
$l_1$, and $l_2$ are all linear in the size of the game tree (number
of states in the game) and such that Nash equilibria correspond to
pairs $(x, y)$ of \textit{realization plans} which solve the primal
LCP (Linear Convex Program)
\begin{equation}
  \begin{aligned}
     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{
       subject to: }(y,p) \in \mathbb{R}^{n_2} \times
     \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

@@

%% Note that $\langle e_1, p\rangle = p_0$ and $\langle e_2, q\rangle
%% = q_0$ by definition of $e_1$ and
%% $e_2$. 
At a feasible point $(y, p, x, q)$, the \textit{primal-dual gap}
$\tilde{G}(y, p, x, q)$ of these primal-dual pair of LCPs is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{eqnarray}
  \begin{split}
  0 \le \tilde{G}(y, p, x, q) &:= \langle e_1, p\rangle - (-\langle
  e_2, q\rangle) = \langle e_1, p\rangle + \langle
  e_2, q\rangle\\
  &= G(x, y) := \mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle |
(u,v) \in Q_1 \times Q_2\}.
\end{split}
  \label{eq:dgap}
\end{eqnarray}

It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
$(x, y) \in Q_1 \times Q_2$ of realization plans is a solution to the
LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a Nash
equilibrium for the game)  if and only if there exist vectors $p$ and
$q$ such that
\begin{equation}
\hspace{.25em} -Ay + E_1^Tp \ge 0, \hspace{.5em}A^Tx + E_2^Tq \ge
0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0, \hspace{.25em}
\langle y, A^Tx  + E_2^Tq\rangle = 0.
\label{eq:feasibility}
\end{equation}

@@

Developing on an alternative notion of approximate equilibria (see
Definition \ref{thm:cool_notion})
homologuous to that presented in Definition \ref{thm:approx_nash}, we
device a primal-dual algorithm (Algorithm \ref{Tab:algo}) for
computing approximate Nash equilibria in sequential two-person
zero-sum games with imcomplete information and perfect recall. We also
prove (Theorem \ref{thm:pd})
that the number of iterations required by the algorithm to
produce an approximation equilibrium to a precision $\epsilon$ is
$\mathcal{O}(1/\epsilon)$.%%  The source of approximation in our scheme
%% is that we explicitly control how close we are to the feasible set
%% $Q_1 \times Q_2$.

\section{Related work}
\label{sec:related_work}
We present a selection of algorithms that is representative of the
efforts that have been made in the literature to compute Nash
$\epsilon$-equilibria for two-person zero-sum games with imcomplete
information like Texas Hold'em Poker, etc.

@@

The primal-dual algorithm first developed in \cite{chambolle2010} was
proposed \cite{chambolle2014ergodic} in to solve matrix games on
simplexes. It should be stressed that such matrix games are
considerably simpler than the games considered here. Indeed, the
authors in \cite{chambolle2014ergodic} use the fact that computing the
euclidean projection of a point unto a simplex can be done in linear
time as in \cite{duchi2008efficient}. In contrast, no such efficient
algorithm is known nor is likely to exist for the polyhedra $Q_k$
defined in \eqref{eq:polyhedron}, the strategy profiles for players in
the games considered here. It should however be noted that such this
projection can still be done iteratively using, for example, the
algorithm in proposition 4.2 of \cite{combettes2010dualization} or the
algorithms developed in \cite{tran2015splitting}. Unfortunately, as
with any nested iterative scheme, one would have to solve this
sub-problem with finer and finer precision.

Sampling techniques like the CFR (CounterFactual Regret minimization)
and its many variants
\cite{MartinZinkevichNIPS2007,lanctot2009monte,Bowling09012015} have
also become state-of-the-art.

Finally, let us note that for the class of games considered here
(sequential games with imcomplete information), the LCPs
\eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger
than what state-of-the-art LCP and interior-point solvers can
handle. See for example \cite{hoda2010smoothing}.

\section{Methods}
\subsection{The Generalized Saddle-point Problem (GSP) connection}
\label{sec:gsp}
In the next theorem, we show that the LCPs \eqref{eq:primal_pb}
and \eqref{eq:dual_pb} can be
conveniently written as a \textit{Generalized Saddle-point Problem
  (GSP)} in the sense of \cite{he2013accelerating}.
\begin{theorem}
Define two proper closed convex functions
  \begin{eqnarray}
    \left.
    \begin{aligned}
      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
        i_{y \ge 0} + \langle e_1,p\rangle\\
        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
          i_{x \ge 0} + \langle e_2, q\rangle
    \end{aligned}
    \right\}
    \label{eq:things}
  \end{eqnarray}

@@

\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with imcomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\epsilon,0)$-equilibrium
$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k
\leftarrow 0$
\While{$\|{v}_{a}^{(k)}\|/k \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$, \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$, \hspace{.5em}$\Delta x^{(k+1)} \leftarrow
x^{(k+1)}-x^{(k)}$
\State $\Delta q^{(k+1)} \leftarrow \lambda (E_2y -
e_2)$, \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
+ E_2^T\Delta q^{(k+1)})$, \hspace{.5em}$\Delta y^{(k+1)} \leftarrow
y^{(k+1)}-y^{(k)}$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$,
\hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} +
\frac{1}{\lambda}(\Delta
y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

\section{Experimental results}
\label{sec:results}
To access the practical quality of the proposed algorithm, we
tested it on simulated and real games.
\paragraph{\textit(a) Experiments on sequential games with imcomplete
  information: Kuhn 3-card
  poker.} This game is a simplified form of poker
developed by Harold W. Kuhn. It is a two-person zero-sum game which is
simply enough to serve as an example but contains all the complexity
traits of a imcomplete information sequential game. The
deck includes only three playing cards, for example a King, Queen, and
Jack. One card is dealt to each player, then the first player must bet
or pass, then the second player may bet or pass. If any player chooses
to bet the opposing player must bet as well ("call") in order to stay
in the round. After both players pass or bet the player with the
highest card wins the pot. The
sequence-form representation of the game has $n_1 = n_2 = 13$
sequences and $l_1 = l_2 = 7$ information
sets per player. The sequence-form of the game is given by\\\\
$E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
E_1(5,5) = E_1(6,9) = {-1}$; $E_2 \in \mathbb{R}^{7 \times 13}$ with
$E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
E_2(5,0) = E_2(6,0) = {-1}$; and $A \in \mathbb{R}^{13 \times
  13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
$A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
A(12,1) = A(12,5) = {0.166667}$.\\

@@

\begin{figure}[!htpb]
  \subfigure[$10^3 \times 10^3$ matrix game on simplexes]{
    \includegraphics[width=.5\linewidth]{0.pdf}
  }
  %% \hspace{-2em}
  %% \subfigure[Toy Poker]{
  %%   \includegraphics[width=.5\linewidth]{SimplifiedPoker_dgap.pdf}
  %% }
  \hspace{-2em}
  \subfigure[Kuhn 3-card poker]{
    \includegraphics[width=.5\linewidth]{Kuhn3112_dgap.pdf}
  }
  \vspace{-1em}
  \hspace{-.5em}
  \includegraphics[width=.5\linewidth]{1.pdf}
  %% \hspace{-1em}
  %% \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
  %\hspace{.5em}
  \includegraphics[width=.49\linewidth]{Kuhn3112_NE.pdf}
  \caption{Convergence curves of Algorithm
    \ref{Tab:algo}. In \textit{(a)}, the duality gaps
    are computed according to formula \eqref{eq:mg_pd}. One can see
    the linear (i.e exponential) behavior of the algorithm in
    \cite{gilpinfirst}, inbetween consecutive breakpoints on the
    $\epsilon$ grid (though the rate of exponential growth seems to by
    quite close to $1$ here). The first-order smoothing algorithm from
    \cite{nesterov2005a} jitters around as the iterations go on
    because even the smoothed problem becomes heavily ill-conditioned
    near solutions. On the other hand, our proposed
    algorithm seems to beat both of the aforementioned algorithms, and
  its proven $\mathcal{O}(1/\epsilon)$ convergence rate is clearly
  verified empirically.}
  \label{Tab:dgap_curve}
\end{figure}

\section{Concluding remarks}
Making use of the sequence-form representation
\cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
deviced a simple and efficient primal-dual algorithm for computing
Nash equilibria in two-person zero-sum sequential games with
imcomplete information (like Texas Hold'em, etc.). Our algorithm is
simple to implement, with a low constant cost per iteration, and
enjoys a rigorous convergence theory with a proven
$\mathcal{O}(1/\epsilon)$ convergence in terms of basic operations
(matvec products, clipping, etc.), to a Nash
$(\epsilon,0)$-equilibrium of the game. Equilibrium problems are
saddle-point convex-concave problems, and as
such a natural choice for algorithms for solving them would be in the
family of primal-dual algorithms. We believe such primal-dual
schemes will receive more attention in the algorithmic game theory
community in future.

>>>>

\title{
  %\hrule\hrule\bigskip\bigskip
  A simple and efficient algorithm for computing approximate
  Nash equilibria in sequential games with imcomplete
  information}
\author{Elvis DOHMATOB, Gael VAROQUAUX, Bertrand THIRION
\\\\Parietal team, Inria Saclay Ile-de-France, Saclay, France
\\\texttt{firstname.lastname@inria.fr}
}

@@

\maketitle
\begin{abstract}We present a simple primal-dual algorithm for
  computing approximate Nash equilibria in two-person zero-sum
  sequential games with  incomplete information and perfect recall
  (like Texas Hold'em Poker). Our algorithm only performs basic
  iterations (i.e iterations involving no calls to external
  first-order oracles, etc.)
  and is applicable to a broad class of two-person zero-sum games
  including simultaneous games and sequential games with incomplete
  information and perfect recall. The applicability to the latter kind
  of games is thanks to the sequence-form representation
  \cite{koller1992complexity} which allows us to encode any such game
  as a matrix game with polyhedral strategy profiles. We prove that
  the number of iterations needed to produce a Nash equilibrium with a
  given precision is inversely proportional to the
  precision. We also present experimental results on simulated and
  real games (Kuhn poker).
\end{abstract}

\textbf{keywords}: sequential game; incomplete information; perfect
recall; approximate Nash equilibrium; primal-dual
algorithm; convex-optimization

\section{Introduction}
\label{sec:intro}
A game-theoretic approach to playing games strategically optimally
consists in computing Nash-equilibria (infact, approximations thereof)
offline, and playing one's part (an optimal \textit{behavioral}
strategy) of the equilibrium online. This
technique is the driving-force behind solution concepts like CFR
\cite{zinkevich2008regret,lanctot2009monte,Bowling09012015},
$\text{CFR}^{+}$ \cite{tammelin14} and other variants, etc., which
have recently had profound success in Poker. However, solving games
for equilibria remains a mathematical and computational challenge,
especially in sequential games with imperfect information. This paper
proposes a simple and efficient algorithm for solving for such
equilibria approximately, in a sense which will be made clear shortly.

@@

\subsection{Nash-equilibrium concepts and statement of the problem}
The sequence-form representation for two-person zero-sum games with
incomplete information was introduced in
\cite{koller1992complexity}, and the theory was further developed in
\cite{koller1994fast,von1996efficient,vonequilibrium} where it was
established that for such games, there exist sparse matrices
$A \in \mathbb{R}^{n_1 \times n_2}$, $E_1 \in \mathbb{R}^{l_1 \times
  n_1}$, $E_2 \in \mathbb{R}^{l_2 \times n_2}$, and vectors $e_1 \in
\mathbb{R}^{l_1}, e_2 \in \mathbb{R}^{l_2}$ such that $n_1$, $n_2$,
$l_1$, and $l_2$ are all linear in the size of the game tree (number
of states in the game) and such that Nash equilibria correspond to
pairs $(x, y)$ of \textit{realization plans} which solve the primal
LCP (Linear Convex Program)
\begin{equation}
  \begin{aligned}
     \text{minimize }\langle e_1, p\rangle, \hspace{.5em}\text{
       subject to: }(y,p) \in \mathbb{R}^{n_2} \times
     \mathbb{R}^{l_1},  y \ge 0, E_2y = e_2, -Ay + E_1^Tp \geq 0.
  \end{aligned}
  \label{eq:primal_pb}
\end{equation}

@@

%% Note that $\langle e_1, p\rangle = p_0$ and $\langle e_2, q\rangle
%% = q_0$ by definition of $e_1$ and
%% $e_2$. 
At a feasible point $(y, p, x, q)$ for the LCPs, the \textit{primal-dual gap}
$\tilde{G}(y, p, x, q)$ of these primal-dual pair is given
by\footnote{The inequality being due to \textit{weak duality}.}
\begin{eqnarray}
  \begin{split}
  0 \le \tilde{G}(y, p, x, q) &:= \langle e_1, p\rangle - (-\langle
  e_2, q\rangle) = \langle e_1, p\rangle + \langle
  e_2, q\rangle\\
  &= G(x, y) := \mathrm{max}\{\langle u, Ay\rangle - \langle x, Av\rangle |
(u,v) \in Q_1 \times Q_2\}.
\end{split}
  \label{eq:dgap}
\end{eqnarray}
In \eqref{eq:dgap}, the quantity $G(x, y)$ is nothing but the primal-dual
gap for the equivalent saddle point problem \eqref{eq:gilpin}.
It was shown (see Theorem 3.14 of \cite{vonequilibrium}) that a pair
$(x, y) \in Q_1 \times Q_2$ of realization plans is a solution to the
LCPs \eqref{eq:primal_pb} and \eqref{eq:dual_pb} (i.e is a Nash
equilibrium for the game)  if and only if there exist vectors $p$ and
$q$ such that
\begin{equation}
\hspace{.25em} -Ay + E_1^Tp \ge 0, \hspace{.5em}A^Tx + E_2^Tq \ge
0, \hspace{.25em} \langle x, -Ay + E_1^Tp\rangle = 0, \hspace{.25em}
\langle y, A^Tx  + E_2^Tq\rangle = 0.
\label{eq:feasibility}
\end{equation}

@@

Developing on an alternative notion of approximate equilibria (see
Definition \ref{thm:cool_notion})
homologuous to that presented in Definition \ref{thm:approx_nash}, we
device a primal-dual algorithm (Algorithm \ref{Tab:algo}) for
computing approximate Nash equilibria in sequential two-person
zero-sum games with incomplete information and perfect recall. We also
prove (Theorem \ref{thm:pd})
that the number of iterations required by the algorithm to
produce an approximation equilibrium to a precision $\epsilon$ is
$\mathcal{O}(1/\epsilon)$. These contributions will be elaborated in
section \ref{sec:gsp}. %%  The source of approximation in our scheme
%% is that we explicitly control how close we are to the feasible set
%% $Q_1 \times Q_2$.

\section{Related work}
\label{sec:related_work}
We present a selection of algorithms that is representative of the
efforts that have been made in the literature to compute Nash
$\epsilon$-equilibria for two-person zero-sum games with incomplete
information like Texas Hold'em Poker, etc.

First and foremost, let us note that for the class of games considered
here (sequential games with incomplete information), the LCPs
\eqref{eq:primal_pb} and \eqref{eq:dual_pb} are exceedingly larger
than what state-of-the-art LCP and interior-point solvers can
handle. See for example \cite{hoda2010smoothing,gilpinfirst}.

@@

The primal-dual algorithm first developed in \cite{chambolle2010}, was
proposed can be used to solve matrix games on
simplexes as was done in \cite{chambolle2014ergodic}, for example.
It should be stressed that such matrix games are
considerably simpler than the games considered here. Indeed, the
authors in \cite{chambolle2014ergodic} use the fact that computing the
euclidean projection of a point onto a simplex can be done in linear
time as in \cite{duchi2008efficient}. In contrast, no such efficient
algorithm is known nor is likely to exist for the polyhedra $Q_k$
defined in \eqref{eq:polyhedron}, the strategy profiles for players in
the games considered here. It should however be noted that such this
projection can still be done iteratively using, for example, the
algorithm in proposition 4.2 of \cite{combettes2010dualization} or the
algorithms developed in \cite{tran2015splitting}. Unfortunately, as
with any nested iterative scheme, one would have to solve this
sub-problem with finer and finer precision.

Sampling techniques like the CFR (CounterFactual Regret minimization)
\cite{zinkevich2008regret,lanctot2009monte,Bowling09012015} have
also become state-of-the-art, and are particularly useful in
many-player games, since convex-analytical methods cannot help much in
such games.

\section{Methods}
\label{sec:gsp}
\subsection{The Generalized Saddle-point Problem (GSP) connection}
In the next theorem, we show that the LCPs \eqref{eq:primal_pb}
and \eqref{eq:dual_pb} can be
conveniently written as a \textit{Generalized Saddle-point Problem
  (GSP)} in the sense of \cite{he2013accelerating}.
\begin{theorem}
Define two proper closed convex functions
  \begin{eqnarray}
    \left.
    \begin{aligned}
      g_1: \mathbb{R}^{n_2} &\times \mathbb{R}^{l_1} \rightarrow
      (-\infty, +\infty], \hspace{1em} g_1(y, p) :=
        i_{y \ge 0} + \langle e_1,p\rangle\\
        g_2: \mathbb{R}^{n_1} &\times \mathbb{R}^{l_2} \rightarrow
        (-\infty, +\infty],\hspace{1em} g_2(x, q) :=
          i_{x \ge 0} + \langle e_2, q\rangle
    \end{aligned}
    \right\}
    \label{eq:things}
  \end{eqnarray}

@@

\begin{algorithm}
\caption{Primal-dual algorithm for computing approximate Nash
  Equilbria in two-person zero-sum games with incomplete information
  and perfect recall}
\label{Tab:algo}
\begin{algorithmic}[1]
\Require $\epsilon > 0$; $(y^{(0)},p^{(0)},x^{(0)},q^{(0)})
\in \mathbb{R}^{n_2}
  \times \mathbb{R}^{l_1} \times \mathbb{R}^{n_1} \times
  \mathbb{R}^{l_2}$.
\Ensure A Nash $(\epsilon,0)$-equilibrium
$({y^*},{p^*},{x^*},{q^*}) \in S_1 \times S_2$ for
the GSP \eqref{eq:unconstrained_pb}.
\State  $\lambda \leftarrow 1/\|K\|$, ${v}_a^{(0)} \leftarrow 0$, $k
\leftarrow 0$
\While{$\|{v}_{a}^{(k)}\|/k \ge \epsilon$}
\State $y^{(k + 1)} \leftarrow (y^{(k)} - \lambda (A^Tx^{(k)} +
E_2^Tq^{(k)}))_+$, \hspace{.5em}$p^{(k+1)} \leftarrow p^{(k)} -
\lambda(e_1-E_1x^{(k)})$
\State $x^{(k + 1)} \leftarrow (x^{(k)} + \lambda (Ay^{(k+1)} -
E_1^Tp^{(k+1)}))_+$, \hspace{.5em}$\Delta x^{(k+1)} \leftarrow
x^{(k+1)}-x^{(k)}$
\State $\Delta q^{(k+1)} \leftarrow \lambda (E_2y -
e_2)$, \hspace{.5em}$q^{(k+1)} \leftarrow q^{(k)} + \Delta q^{(k+1)}$
\State $y^{(k+1)} \leftarrow y^{(k+1)} - \lambda (A^T\Delta x^{(k+1)}
+ E_2^T\Delta q^{(k+1)})$, \hspace{.5em}$\Delta y^{(k+1)} \leftarrow
y^{(k+1)}-y^{(k)}$
\State $p^{(k+1)} \leftarrow p^{(k+1)} + \lambda E_1\Delta x^{(k+1)}$,
\hspace{.5em} $\Delta p^{(k+1)} \leftarrow p^{(k+1)}-p^{(k)}$
\State ${v}_a^{(k+1)} \leftarrow {v}_a^{(k)} +
\frac{1}{\lambda}(\Delta
y^{(k+1)},\Delta p^{(k+1)},\Delta x^{(k+1)},\Delta q^{(k+1)})$
\State $k \leftarrow k + 1$
\EndWhile
\end{algorithmic}
\end{algorithm}

@@

\section{Experimental results}
\label{sec:results}
To access the practical quality of the proposed algorithm, we
tested it on simulated and real games.
\paragraph{\textit(a) Experiments on sequential games with incomplete
  information: Kuhn 3-card
  poker.} This game is a simplified form of poker
developed by Harold W. Kuhn. It is a two-person zero-sum game which is
simply enough to serve as an example but contains all the complexity
traits of a incomplete information sequential game. The
deck includes only three playing cards, for example a King, Queen, and
Jack. One card is dealt to each player, then the first player must bet
or pass, then the second player may bet or pass. If any player chooses
to bet the opposing player must bet as well ("call") in order to stay
in the round. After both players pass or bet the player with the
highest card wins the pot. The
sequence-form representation of the game has $n_1 = n_2 = 13$
sequences and $l_1 = l_2 = 7$ information
sets per player. The sequence-form of the game is given by\\\\
$E_1 \in \mathbb{R}^{7 \times 13}$ with $E_1(0,0) = E_1(1,9) =
E_1(1,12) = E_1(2,1) = E_1(2,4) = E_1(3,5) =
E_1(3,8) = E_1(4,2) = E_1(4,3) = E_1(5,6) = E_1(5,7) = E_1(6,10) =
E_1(6,11) = {1}$, $E_1(1,0) = E_1(2,0) = E_1(3,0) = E_1(4,1) =
E_1(5,5) = E_1(6,9) = {-1}$; $E_2 \in \mathbb{R}^{7 \times 13}$ with
$E_2(0,0) = E_2(1,7) = E_2(1,8) = E_2(2,9) = E_2(2,10) = E_2(3,5) =
E_2(3,6) = E_2(4,11) = E_2(4,12) = E_2(5,1) = E_2(5,2) = E_2(6,3) =
E_2(6,4) = {1}$, $E_2(1,0) = E_2(2,0) = E_2(3,0) = E_2(4,0) =
E_2(5,0) = E_2(6,0) = {-1}$; and $A \in \mathbb{R}^{13 \times
  13}$ with $A(3,8) = A(3,12) = A(4,6) = A(4,10) = A(7,12) = A(8,10) =
{-0.333333}$, $A(1,7) = A(1,11) = A(2,8) = A(2,12) = A(5,11) =
A(6,4) = A(6,12) = A(10,4) = A(10,8) = {-0.166667}$, $A(7,4) =
A(8,2) = A(11,4) = A(11,8) = A(12,2) = A(12,6) = {0.333333}$,
$A(4,5) = A(4,9) = A(5,3) = A(8,1) = A(8,9) = A(9,3) = A(9,7) =
A(12,1) = A(12,5) = {0.166667}$.\\

@@

\begin{figure}[!htpb]
  \subfigure[$10^3 \times 10^3$ matrix game on simplexes]{
    \includegraphics[width=.5\linewidth]{0.pdf}
  }
  %% \hspace{-2em}
  %% \subfigure[Toy Poker]{
  %%   \includegraphics[width=.5\linewidth]{SimplifiedPoker_dgap.pdf}
  %% }
  \hspace{-2em}
  \subfigure[Kuhn 3-card poker]{
    \includegraphics[width=.5\linewidth]{Kuhn3112_dgap.pdf}
  }
  \vspace{-1em}
  \hspace{-.5em}
  \includegraphics[width=.5\linewidth]{1.pdf}
  %% \hspace{-1em}
  %% \includegraphics[width=.5\linewidth]{SimplifiedPoker_NE.pdf}
  %\hspace{.5em}
  \includegraphics[width=.49\linewidth]{Kuhn3112_NE.pdf}
  \caption{Convergence curves of Algorithm
    \ref{Tab:algo}. In \textit{(a)}, the duality gaps
    are computed according to formula \eqref{eq:mg_pd}. One can see
    the linear (i.e exponential) behavior of the algorithm in
    \cite{gilpinfirst}, inbetween consecutive breakpoints on the
    $\epsilon$ grid (though the rate of exponential growth seems to by
    quite close to $1$ here). The first-order smoothing algorithm from
    \cite{nesterov2005a} jitters around as the iterations go on
    because even the smoothed problem becomes heavily ill-conditioned
    near solutions. On the other hand, our proposed
    algorithm beats both of the aforementioned algorithms, and
  its proven $\mathcal{O}(1/\epsilon)$ convergence rate is clearly
  verified empirically.}
  \label{Tab:dgap_curve}
\end{figure}

\section{Concluding remarks}
Making use of the sequence-form representation
\cite{koller1992complexity,von1996efficient,vonequilibrium}, we have
deviced a simple and efficient primal-dual algorithm for computing
Nash equilibria in two-person zero-sum sequential games with
incomplete information (like Texas Hold'em, etc.). Our algorithm is
simple to implement, with a low constant cost per iteration, and
enjoys a rigorous convergence theory with a proven
$\mathcal{O}(1/\epsilon)$ convergence in terms of basic operations
(matvec products, clipping, etc.), to a Nash
$(\epsilon,0)$-equilibrium of the game. Equilibrium problems are
saddle-point convex-concave problems, and as
such a natural choice for algorithms for solving them would be in the
family of primal-dual algorithms. We believe such primal-dual
schemes will receive more attention in the algorithmic game theory
community in future.
